Working title: Ecological network control

### 2018-06-17 paper/manuscript.Rmd
Controllability section in results

```{r controllability}
drake::loadd(controllability, metadata)
c_m <- controllability %>% 
  filter_networks_df(metadata)
```

The size of the minimum driver node set relative to the number of species in each network $n_D$ ranged between $n_D = `r round(min(c_m$n_D), 2)`$ and $n_D = `r round(max(c_m$n_D), 2)`$ (median `r round(median(c_m$n_D), 2)`, Figure \@ref(fig:fig-emp-controllability)). 
We found that the relative size of the minimum driver node set was not related to any of our independent variables. 
Indeed the null model ($n_D \sim 1$) was the most parsimonious candidate model and all variables were relatively unimportant (based on the AICc; Supplementary Information \@ref(S-controllability-models)).

>>>>

```{r controllability}
drake::loadd(controllability, metadata, randomisations_test)
c_m <- controllability %>% 
  filter_networks_df(metadata)
```

The size of the minimum driver node set relative to the number of species in each network $n_D$ ranged between $n_D = `r round(min(c_m$n_D), 2)`$ and $n_D = `r round(max(c_m$n_D), 2)`$ (median `r round(median(c_m$n_D), 2)`, Figure \@ref(fig:fig-emp-controllability)a). 
We found that the relative size of the minimum driver node set was not related to any of the independent variables we evaluated. 
Indeed the null model ($n_D \sim 1$) was the most parsimonious candidate model and all variables were relatively unimportant (based on the AICc; Supporting Information Section \@ref(S-controllability-models)). 
The $n_D$ of empirical networks did not differ to that of a null model that roughly preserved the degree distribution and fully preserved the network connectance ($p = `r sprintf('\\num{%s}', format(randomisations_test$interactions$p.value, digits = 2))`$; Figure \@ref(fig:fig-emp-controllability)b). 
However empirical networks had a larger $n_D$ than null models that preserved the interactions but shuffled the direction of control of the empirical network ($p = `r sprintf('\\num{%s}', format(randomisations_test$directions$p.value, digits = 2))`$).
